Supporting Information\\ \textit{Cross Validation Approaches for Penalized Cox Regression}

### 2023-01-05 sub/smimr/response.tex

\end{enumerate}

\newpage

\subsubsection*{Response to comments by Reviewer \#2}

Thank you very much for your careful reading of the paper and your insightful comments, particularly regarding the cross-validated deviance residuals. This was the weakest aspect of the original submission, and by putting thought and work into addressing the issues you raised, we feel that we have significantly improved the manuscript.

### 2023-01-05 main.tex
p to p-value
Revisions to final paragraph of discussion

\begin{table}[ht]
\centering
\caption{\label{Tab:go} Five most significantly enriched molecular functions among genes selected by the linear predictor method with the elastic net ($\alpha=0.3$).  The five terms have a false discovery rate of 3\% using the Benjamini-Hochberg method. Enrichment: frequency of the annotation among the selected genes divided by its frequency in the genome as a whole.}
\begin{tabular}{llrrr}
\toprule
ID & Name & Selected & Enrichment & p \\
\midrule
GO:0008134 & transcription factor binding & 10 & 4.1 & 0.00015 \\
GO:0035257 & nuclear hormone receptor binding & 5 & 7.4 & 0.00057 \\
GO:0019869 & chloride channel inhibitor activity & 2 & 53.2 & 0.00061 \\
GO:0003700 & DNA-binding transcription factor activity & 14 & 2.6 & 0.00068 \\
GO:0005102 & signaling receptor binding & 16 & 2.4 & 0.00083 \\
\bottomrule
\end{tabular}
\end{table}

@@

Although we focused upon the penalized Cox regression with a LASSO penalty in this work, the methods that we analyzed are applicable in any context that involves conducting model selection for survival models that are built upon the Cox partial likelihood, such fitting penalized Cox regression with other penalty functions (elastic net \citep{Zou2005}, SCAD\citep{FanLi2001}, MCP\citep{Zhang2010}, precision lasso\citep{Wang2018}) and penalty structures (group selection, bi-level selection), selecting functional forms of covariates in unpenalized Cox regression, model selection for unpenalized Cox regression that involve time-varying covariates and longitudinal covariates. Since all the cross-validation approaches that are discussed in this manuscript depend on the Cox partial likelihood, they are subject to limitations such as non-proportional hazards and rare events that are tied to the Cox proportional hazard model.

>>>>

\begin{table}[ht]
\centering
\caption{\label{Tab:go} Five most significantly enriched molecular functions among genes selected by the linear predictor method with the elastic net ($\alpha=0.3$).  The five terms have a false discovery rate of 3\% using the Benjamini-Hochberg method. Enrichment: frequency of the annotation among the selected genes divided by its frequency in the genome as a whole.}
\begin{tabular}{llrrr}
\toprule
ID & Name & Selected & Enrichment & $p$-value \\
\midrule
GO:0008134 & transcription factor binding & 10 & 4.1 & 0.00015 \\
GO:0035257 & nuclear hormone receptor binding & 5 & 7.4 & 0.00057 \\
GO:0019869 & chloride channel inhibitor activity & 2 & 53.2 & 0.00061 \\
GO:0003700 & DNA-binding transcription factor activity & 14 & 2.6 & 0.00068 \\
GO:0005102 & signaling receptor binding & 16 & 2.4 & 0.00083 \\
\bottomrule
\end{tabular}
\end{table}

@@

Although we focused upon the penalized Cox regression with a LASSO penalty in this work, the methods that we analyzed are applicable in any context that involves conducting model selection for survival models that are built upon the Cox partial likelihood, such fitting penalized Cox regression with other penalty functions (elastic net \citep{Zou2005}, SCAD \citep{FanLi2001}, MCP \citep{Zhang2010}, precision lasso \citep{Wang2018}), other penalty structures (group selection, bi-level selection), and selecting functional forms of covariates in unpenalized Cox regression. We note, however, that the focus of this article is restricted to fixed covariates. How best to carry out cross-validation for model selection in the presence of time-varying covariates, or in joint modeling of time-to-event and longitudinal outcomes, remains an open question worthy of additional future study.
